Using structural and evolutionary information to detect and correct pyrosequencing errors in non-coding RNAs

### 2013-07-01 JCB/results_JCB.tex
stuff
Minor changes/typos

 \begin{figure}
\centering
\begin{subfigure}{.33\textwidth}
  \centering
  \includegraphics[width=\linewidth]{figures/5fold-b}
  \caption{$5-$fold coverage}
\end{subfigure}%
\begin{subfigure}{.33\textwidth}
  \centering
  \includegraphics[width=\linewidth]{figures/10fold-b}
    \caption{$10-$fold coverage}
\end{subfigure}
\begin{subfigure}{.33\textwidth}
  \centering
  \includegraphics[width=\linewidth]{figures/15fold-b}
    \caption{$15-$fold coverage}
\end{subfigure}
\caption{Performance of error-correction over structured positions (i.e. inside a base pair). Subfigures show accuracy when
ART fold parameter is set to 5, 10 and $15-$fold coverage. We also analyze the impact of the parameter $\alpha$ distributing the weights of stacking pair energies vs isostericity scores and use values ranging of $\alpha = \{0, 0.5, 0.8, 1.0\}$. The AUC is indicated in the legend of the figures. Each individual ROC curve represent the average performance over at least 10 experiments.}
\label{fig:16s_bp}
\end{figure}

@@

An interesting feature is that best results are almost always when $\alpha=0$, i.e. all the contribution
comes from the isostericity. A notable exception is when the number of mutation is underestimated, 
in that case best performances were observed for non-null values of $\alpha$.

Another observation is when we look at all positions as in Fig.~\ref{fig:16s_all}. The first $20\%$ to $30\%$ of sensitivity are obtained almost without any errors and correspond to the nucleotides in 
structured regions. The rest of the predictions are done on un-paired nucleotides.

>>>>

 \begin{figure}
\centering
\begin{subfigure}{.33\textwidth}
  \centering
  \includegraphics[width=\linewidth]{figures/5fold-b}
  \caption{$5-$fold coverage}
\end{subfigure}%
\begin{subfigure}{.33\textwidth}
  \centering
  \includegraphics[width=\linewidth]{figures/10fold-b}
    \caption{$10-$fold coverage}
\end{subfigure}
\begin{subfigure}{.33\textwidth}
  \centering
  \includegraphics[width=\linewidth]{figures/15fold-b}
    \caption{$15-$fold coverage}
\end{subfigure}
\caption{Performance of error-correction restricted to structured positions (i.e. involved in a canonical base pair). Subfigures show accuracy when
ART fold parameter is set to 5, 10 and $15-$fold coverage. We also analyze the impact of the parameter $\alpha$ distributing the weights of stacking pair energies vs isostericity scores and use values ranging of $\alpha = \{0, 0.5, 0.8, 1.0\}$. The AUC is indicated in the legend of the figures. Each individual ROC curve represent the average performance over at least 10 experiments.}
\label{fig:16s_bp}
\end{figure}

@@

An interesting feature is that best results are almost always when $\alpha=0$, i.e. all the contribution
comes from the isostericity. A notable exception is when the number of mutation is underestimated, 
in that case best performances were observed for larger values of $\alpha$.

A final observation is related to  all positions as in Fig.~\ref{fig:16s_all}. The first $20\%$ to $30\%$ of sensitivity are obtained almost without any errors and correspond to the nucleotides in 
structured regions. The rest of the predictions are done on un-paired nucleotides.
